 
## Amazon Web Services (AWS)

### How to get the shell for the Amazon EC2 instance?

% ssh -i ~/Downloads/key.pem <name-of_EC2-Instance>

### How to setup Amazon EC2 for R?

Visit www.louisaslett.com for the instructions.

### How to create a new file system (new entry under /dev)?

```{r, eval=FALSE}
#list the blocks
lsblk

#create new file system
sudo mkfs -t ext4 /dev/xvdf
```

### How to create a mount point?

```{r, eval = FALSE}

# create the mount point
%sudo mkdir mount_point_name 

ex: sudo mkdir /data

# mount it
%sudo mount /dev/xvdf /data
```


### How to download the dataset directly to the EC2 instance from kaggle?

%wget -x -c --load-cookies /home/rstudio/cookies.txt http://www.kaggle.com/c/grupo-bimbo-inventory-demand/download/test.csv.zip

### How to get the secured shell?

```{r, eval=FALSE}
ssh -i ~/Downloads/aws.pem login@DNS

Ex:
ssh -i ~/Downloads/aws.pem ubuntu@ec2-blah-blah.compute.amazonaws.com

```

### How to see the session through broswer?

```{r, eval=FALSE}
#In the browser type in the DNS.
Ex: ec2-blah-blah.compute.amazonaws.com

Based on the AMI (amazon image) & login credentials, get into the session.
ex: for id/passwd: rstudio / rstudio.
```

### How to copy the files from desktop to remote machine?

```{r, eval=FALSE}
#use secured copy

# similar to ssh
scp -i ~/Downloads/aws.pem file.csv login@machine:destination-location

Ex: scp -i ~/Downloads/aws.pem file.csv ubuntu@ec2-blah-blah-DNS:/home/rstudio/mydata
```
