---
title: "R Gotchas"
author: "Anandan Balaji"
output: 
  html_document:
    toc: yes
    number_sections: 2
---

#Gotchas related to R

## How to run RScript in the iinux shell?
   RScript script-name
   
## How to save the plots to the disk?
   Follow the below code snippet.
   
   jpgeg(filename = "plot1.jpeg")
   
   ggplot(...)
   
   dev.off()
   
   or 
   Use Export option in the RStudio.
   
## Language specific feature
   * R is case sensitive
   * The index starts with 1 
   * Use combine syntax c() to creat list. Ex: c(2,4)
   * For assignment, use <-   # temp <- mtcars$mpg
   * No negative indexing. Minus means, skip that.
     mtcars[, -1]  # all rows and skip first column
## How to analyze the data set using R?

### Reading the dataset

  *  Use fread()
```{r eval=FALSE}
    library(data.table)
    system(dt <- fread("./train.csv", header = TRUE))
```

  *  How to read the big dataset?
    
    If you are unable to read the complete dataset due to machine resource issues, restrict the training dataset to small. You can create smaller training dataset for early data analysis in the following ways
    
     *  Use caTools
     
```{r eval=FALSE}
# for splitting the training data
library(caTools)

# data is 3GB
# use partial info for early analysis.
#to make it reproducible
set.seed(123)

## specify the column name
split = sample.split(dt$Cliente_ID, SplitRatio = 0.15)

new_train_dt = subset(dt, split == TRUE)
write.csv(new_train_dt, file = "new_train.csv", row.names = FALSE, quote = FALSE)
```
     
       *  Use dplyr package
     
```{r eval=FALSE}
system(dt <- fread("./train.csv", header = TRUE))

library("dplyr")
new_train <- sample_frac(dt, 0.15) # get only the 15 percent of the training set
write.csv(new_train, file = "new_train.csv", row.names = FALSE, quote = FALSE)

system(dt <- fread("./new_train.csv", header = TRUE))
```

     
### Get the structure of the dataset?
  
```{r eval = FALSE}
str(dt)  # prints the structure of the dataset
rownames(dt)
colnames(dt)

# add new field
dt$newColumn <- dt$col1 + dt$col2

# add new field - use transform
dt <- trainsform(dt, newCol = col1 + col2)
```

### Apply functions

```{r, eval=FALSE}
# apply a function on a data, row wise or column wise
# syntax (data, row / column wise, function)

```

### dplyr functions

#### Order

```{r, eval=FALSR}

# sort based on column margin - this gives the result of the column in the sorted order
companyOrder <- order(companiesData$margin)

# to get the all rows in the sorted order, feed the result from the earlier
companiesOrdered <- companiesData[companyOrder,]

or

# you can do in one line - less readable though
companiesOrdered <- companiesData[order(companiesData$margin),]

# instead of all columns, get me only the few selected cols
companiesOrdered <- companiesData[order(companiesData$margin),c("fy", "company")]

# sort in descending order
companyOrder <- order(-companiesData$margin)

# order based on multiple columns - first one ascedning and second one descending
companiesData[order(companiesData$fy, -companiesData$margin),]


```


#### arrange

```{r, eval=FALSE}
#sort by column name
arrange(dataFrameName, columnName, secondColumnName)
```

### Basic stats

```{r eval=FALSE}
summary(dt)   # prints mean, median etc
cor(dt)       # prints the correlation info in the matrix for the dataframe
cor(dt$dependent_var, dt$independent_var) # correaltion between two specific variables
mean(vector, na.rm = TRUE)  # to remove NA values.
```

### Get slices or subset of data

#### Use $ : dollar symbol
```{r eval=FALSE}
df$column-name  # use $ field name to get the column entrie (mtcars$mpg)
mtcars$mpg > 30  # returns a vector of booleans.
```

#### Use [ : square brackets.

This returns the same class of object.

```{r eval=FALSE}
mtcars[mtcars$mpg > 30]  # return the rows which meets the condition
mtcars[, c(2,4)]  # returns column 2 & 4 for all rows
mtcars[mtcars$mpg>30, c(2,3)] # the rows which meets the condition and return only col 2 & 3
```

#### Use [[  : double square brackets

```{r}
xyz <- list("a", "b", "c", "x", "y")

xyz[3] # this will return the list
xyz[[3]]  # this will return the string "c"

```

# Ploting
```{r}
#install.packages(ggplot2)
library(ggplot2)
```

### Vector of colors

```{r eval=FALSE}
rainbow(n)

heat.colors(n)

terrain.colors(n)

topo.colors(n)

cm.colors(n)
```

### Correlation / Pairwise plot

```{r, eval=FALSE}
library(corrplot)

corrplot(cor(train), type = "upper")

# quick pairwise plot
# scatter plot in matrix format
# just use only 1000 examples and plot only columns 7 thru 11.
pairs(as.data.frame(train)[1:1000, c(7:11)])

```

### Venn Diagram

```{r, eval = FALSE}
library(VennDiagram)
grid.newpage()

training_prod <- unique(train$Producto_ID)
test_prod <- unique(test_dt$Producto_ID)
common_prod <- intersect(training_prod, test_prod)

draw.pairwise.venn(length(training_prod), length(test_prod), length(common_prod), category = c("Traning Products", "Test Products") )
```

### Single variable - Bar plot, histogram

```{r}
#ggplot(mtcars, aes(factor(cyl))) + geom_bar()

mycolors <- heat.colors(3)
ggplot(mtcars, aes(x=factor(cyl))) + geom_bar(fill=mycolors)

#
#ggplot(mydata, aes(x=columnName)) + geom_histogram(binwidth=n)

```


   
### Two variables - Scatter plot, line plot

```{r}

ggplot(mtcars, aes(x=disp, y=mpg)) + geom_point()
```

### Line plot
```{r}
ggplot(pressure, aes(x=temperature, y=pressure)) + geom_line() + geom_point()

```

# Apply function
?help

# Additional Resources
   1. [Advanced R ](http://adv-r.had.co.nz/)
   
   2. [Beautifyl Plotting using R ](http://zevross.com/blog/2014/08/04/beautiful-plotting-in-r-a-ggplot2-cheatsheet-3/)
   
   3. [Computer World](http://www.computerworld.com/article/2497464/business-intelligence/business-intelligence-60-r-resources-to-improve-your-data-skills.html)
   
   
   